### 2012-12-24 inst/examples/myers-exploration.Rmd

```{r Myer-explore}
f <- RickerAllee
p <- c(1.5, 10, 5) 
K <- 10
allee <- 5
# valid only for p[2] = 2
#K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 #
#allee <- p[1] * p[3] / 2 - sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 # allee threshold
#e_star <- (p[1] * sqrt(p[3]) - 2) / 2 ## Bifurcation point 
```

```{r sdp-pars-explore}
sigma_g <- 0.01
sigma_m <- 0.02
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```

>>>>

```{r Myer-explore}
f <- RickerAllee
p <- c(1.1, 10, 5) 
K <- 10
allee <- 5
# valid only for p[2] = 2
#K <- p[1] * p[3] / 2 + sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 #
#allee <- p[1] * p[3] / 2 - sqrt( (p[1] * p[3]) ^ 2 - 4 * p[3] ) / 2 # allee threshold
#e_star <- (p[1] * sqrt(p[3]) - 2) / 2 ## Bifurcation point 
```

```{r sdp-pars-explore}
sigma_g <- 0.05
sigma_m <- 0.02
x_grid <- seq(0, 1.5 * K, length=101)
h_grid <- x_grid
```
